Pillar 2 - Topic Modeling

### 2019-02-28 Pillar 2 - Topic Modeling.Rmd
output LDA models UCM computers

```{r LDA fit, cache = TRUE}
n_topics <- 35
levels   <- c("description", "overview", "manual")
list_nam <- character(0)

for(level in levels){

  dataset   <- get(paste("d", level, "cast", sep = "_"))

  LDA_model <- LDA(
    x       = dataset,
    k       = n_topics,
    method  = "Gibbs",
    control = my_control
    )

  nam <- paste("LDA", level, n_topics, sep = "_")

>>>>

```{r LDA fit, cache = TRUE}
n_topics <- c(35, 35, 40)
levels   <- c("description", "overview", "manual")
list_nam <- character(0)

for(i in seq_along(n_topics)){

  dataset   <- get(paste("d", levels[i], "cast", sep = "_"))

  LDA_model <- LDA(
    x       = dataset,
    k       = n_topics[i],
    method  = "Gibbs",
    control = my_control
    )

  nam <- paste("LDA", levels[i], n_topics[i], sep = "_")
